Modified Silver Ion Chroma

### 2021-01-21 modified_silver_ion_chroma_2.Rmd
updated plots

results <- results %>% 
  mutate(saturation = case_when(
    str_detect(`Peak Name`, "OH") ~ "n0 hydroxy",
    str_detect(`Peak Name`, "cyclo") ~ "n0 cyclo",
    str_detect(`Peak Name`, ":0") ~ "n0",
    str_detect(`Peak Name`, ":2") ~ "n2 cis",
    str_detect(`Peak Name`, "cis") ~ "n1 cis",
    str_detect(`Peak Name`, "trans") ~ "n1 trans",
    str_detect(`Peak Name`, "PAIBE") ~ "PAIBE"
    )
  )
```

@@

p_sfames <- plot_results %>%
  ggplot() +
  aes(`Retention Time`, `Relative Height`, fill = `Peak Name`, key = `Peak Name`) +
  geom_bar(stat = 'identity', width = 0.1)+
  facet_wrap(~fraction_eluent_f, ncol = 1, scales = "free_y") +
  ggtitle("Boulder Soil Free FA as FAMES") +
  theme_bw() +
  theme(legend.position = "none")

>>>>

results <- results %>% 
  mutate(saturation = case_when(
    str_detect(`Peak Name`, "C19 monoene") ~ "C19:1",
    str_detect(`Peak Name`, "cyclo") ~ "n0 cyclo",
    str_detect(`Peak Name`, ":0") ~ "n0",
    str_detect(`Peak Name`, ":2") ~ "n2 cis",
    str_detect(`Peak Name`, "cis") ~ "n1 cis",
    str_detect(`Peak Name`, "trans") ~ "n1 trans",
    str_detect(`Peak Name`, "PAIBE") ~ "PAIBE"
    )
  )
```

@@

p_sfames <- plot_results %>%
  ggplot() +
  aes(`Retention Time`, `Relative Height`, fill = `Peak Name`, key = `Peak Name`) +
  geom_bar(stat = 'identity', width = 0.1)+
  facet_wrap(~fraction_eluent_f, ncol = 1, scales = "free_y") +
  ggtitle("Boulder Soil Free FA as FAMES") +
  theme_bw()
